A Distributed Segment-based Approach for Topology-agnostic Nano Networks Routing

### 2013-09-17 PAPER/simulation.tex
- removed pics

\begin{figure*}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_boot27_Xdefect_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_boot127_Xdefect_Ycoverage.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:coverage}
\end{figure*}

@@

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:bootstrap}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/set1.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/set3.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:coverage}
\end{figure*}

@@

%\begin{figure}
%  \centering
%  \begin{tabular}{cc}
%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
%    (a) & (b)
%  \end{tabular}
%  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
%  \label{fig:bootstrap}
%\end{figure}
